---
title: "HW3"
author: "Zhenning Zhang"
date: '2022-12-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Question 1

Global level git config:
C:/Users/zzn/.gitconfig
(where zzn is my username in English)

Local level git config:
(It's in git repo's .git folder)

And I am using a Windows machine.

(Since I already have an account in my global gitconfig, so I'm no going to override it with UMich account.)

```{r}
system("cat C:/Users/张振宁/.gitconfig")
```

Commands in Git Bash:

pwd
cd Downloads/STATS506/hw3
git init
git add hw3.Rmd
git add .gitignore
git commit

git remote add origin https://github.com/ZhenningZhang/STATS506.git
git branch -M main
git push -u origin main

```{r}
system("cat .gitignore")
```

Question 2

```{r}
# How I technically can read it line by line, ... but fread is really powerful
filepath = "hw3data/2020_Business_Academic_QCQ.txt"
con = file(filepath, "r")
readLines(con, n = 1)
```


```{r}
library(data.table)
```

```{r}
varnames = c("State", "County Code", "Employee Size (5) - Location", "Sales Volume (9) - Location", "Census Tract" )

data = fread(filepath, nrows=10, select=varnames)

data
```





